\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2016-04-08 paper/paper.tex
ref

\subsection{Basic}
The basic algorithm gives all vertices in a graph with the same color but differently colored neighborhoods a separate color. This is done iteratively until the graph has a stable coloring. The determining factor of this method is that all vertices are checked each iteration.

@@

\subsection{Fast}
With fast color refinement the colorsclasses that could be used to refinement other color classes are tracked by putting them in a queue. If a color class is being refined, the class is split into two different classes, with one class keeping the old color. The algorithm terminates with a stable coloring if no color class needs refinement, in other words the queue is empty.

@@

%------------------------------------------------
\section{Algorithms}
\label{app:algs}
\begin{algorithm}
    \begin{algorithmic}[1] % The number tells where the line numbering should start
        \Procedure{BasicColorRefinement}{Graph $G(V,E)$, Coloring $C$}
            \While{not stable} \Comment{Worst case loop over every vertex}
            	 \ForAll{$v \in V$}
            	 	\State calculate $v.nbs$ 
            	  	\If{$v.nbs \neq Q[v.class]$} \Comment{nbs is different from previous iteration}
            	  		\If{$v.nbs \in C$} \Comment{New configuration already has a new color}
            	  			\State Assign $v$ this color
            	  		\Else
            	  			\State $v.class = newColor()$
            	  			\State $C$.add($v.class$)            	  		
            	  		\EndIf
    				\EndIf
            	  \EndFor
				\ForAll{$v \in V)$}
					\State update $C[v]$
				\EndFor
            \EndWhile
        \EndProcedure \Comment{Graph $G$ now has a stable coloring}
    \end{algorithmic}
    \caption{Basic color refinement}
    \label{alg:basic}
\end{algorithm}

@@

    		\EndWhile 
        \EndProcedure
    \end{algorithmic}
    \caption{Fast color refinement}
\end{algorithm}

%------------------------------------------------
\section{Figures}
\label{app:figs}
\begin{multicols}{2}
\begin{figure}[H]
	\includegraphics[width=\linewidth]{basiconly}
	\caption{The computation times of the basic color refinement algorithm for various sizes of the three paths graph.}
	\label{fig:basiconly}
\end{figure}

@@

%------------------------------------------------
% \newpage
\section{Tables} %Change section name
\label{app:tabs}
\begin{table}[h]\centering
\begin{tabular}{|l|r@{.}l|r@{.}l|}
\hline
Graph	
	& \multicolumn{2}{l|}{Basic \emph{(s)}}
	& \multicolumn{2}{l|}{Fast \emph{(s)}} \\
\hline
threepaths\_{}5
	& 0 & 00045
	& 0	& 00059 \\
threepaths\_{}10
	& 0 & 0017
	& 0	& 00086 \\
threepaths\_{}20
	& 0 & 0072
	& 0	& 0018 \\
threepaths\_{}40
	& 0 & 031
	& 0	& 0044 \\
threepaths\_{}80
	& 0 & 126
	& 0	& 0071 \\
threepaths\_{}160
	& 0 & 604
	& 0	& 014 \\
threepaths\_{}320
	& 3 & 213
	& 0	& 029 \\
threepaths\_{}640
	& 19 & 261
	& 0	& 058 \\
threepaths\_{}1280
	& 127 & 567
	& 0	& 117 \\
threepaths\_{}2560
	& 907 & 407
	& 0	& 261 \\
threepaths\_{}5120
	& 5736 & 550
	& 0	& 491 \\
threepaths\_{}10240
	& \multicolumn{2}{c|}{-}
	& 0	& 994 \\
threepaths\_{}10240
	& \multicolumn{2}{c|}{-}
	& 2	& 089 \\

>>>>

\subsection{Basic}
The basic algorithm (Algorithm \autoref{alg:basic}) gives all vertices in a graph with the same color but differently colored neighborhoods a separate color. This is done iteratively until the graph has a stable coloring. The determining factor of this method is that all vertices are checked each iteration.

@@

\subsection{Fast}
With fast color refinement (Algorithm \autoref{alg:fast}) the colorsclasses that could be used to refinement other color classes are tracked by putting them in a queue. If a color class is being refined, the class is split into two different classes, with one class keeping the old color. The algorithm terminates with a stable coloring if no color class needs refinement, in other words the queue is empty.

@@

%------------------------------------------------
\section{Algorithms}
\label{app:algs}
\begin{algorithm}
    \begin{algorithmic}[1] % The number tells where the line numbering should start
        \Procedure{BasicColorRefinement}{Graph $G(V,E)$}
            \While{not stable} \Comment{Worst case loop over every vertex}
            	 \ForAll{$v \in V$}
            	 	\State calculate neighborhood $nbs$ of $v$
            	  	\If {$nbs$ of $v$ has not changed}
    \State pass
    				\Else
    					\ForAll{$u \in V$}
    						\State checks if the configuration is not yet known.
    					\EndFor
    					\If{the configuration is not yet known}
    						\State assign a new color
    					\EndIf
    				\EndIf
            	  \EndFor
				\ForAll{$v \in G(V)$}
					\State update neighborhood dictionary
				\EndFor
            \EndWhile
        \EndProcedure \Comment{Graph $G$ now has a stable coloring}
    \end{algorithmic}
    \caption{Basic color refinement}
    \label{alg:basic}
\end{algorithm}

@@

    		\EndWhile 
        \EndProcedure
    \end{algorithmic}
    \caption{Fast color refinement}
    \label{alg:fast}
\end{algorithm}

%------------------------------------------------
\newpage
\section{Figures}
\label{app:figs}
\begin{multicols}{2}
\begin{figure}[H]
	\includegraphics[width=\linewidth]{basiconly}
	\caption{The computation times of the basic color refinement algorithm for various sizes of the three paths graph.}
	\label{fig:basiconly}
\end{figure}

@@

%------------------------------------------------
\newpage
\section{Tables} %Change section name
\label{app:tabs}
\begin{table}[h]\centering
\begin{tabular}{|l|r@{.}l|r@{.}l|}
\hline
Graph	
	& \multicolumn{2}{l|}{Basic \emph{(s)}}
	& \multicolumn{2}{l|}{Fast \emph{(s)}} \\
\hline
threepaths\_{}5
	& 0 & 00045
	& 0	& 00059 \\
threepaths\_{}10
	& 0 & 0017
	& 0	& 00086 \\
threepaths\_{}20
	& 0 & 0072
	& 0	& 0018 \\
threepaths\_{}40
	& 0 & 031
	& 0	& 0044 \\
threepaths\_{}80
	& 0 & 126
	& 0	& 0071 \\
threepaths\_{}160
	& 0 & 604
	& 0	& 014 \\
threepaths\_{}320
	& 3 & 213
	& 0	& 029 \\
threepaths\_{}640
	& 19 & 261
	& 0	& 058 \\
threepaths\_{}1280
	& 127 & 567
	& 0	& 117 \\
threepaths\_{}2560
	& 907 & 407
	& 0	& 261 \\
threepaths\_{}5120
	& 5736 & 550
	& 0	& 491 \\
threepaths\_{}10240
	& \multicolumn{2}{c|}{-}
	& 0	& 994 \\
threepaths\_{}10240
	& \multicolumn{2}{c|}{-}
	& 2	& 089 \\
